---
title: "Life Sciences Training Data"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

Biochemical_Oxygen_Demand
=========================

```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----
```{r}
Training_Data_List %>%
  filter(Data_set_Name=="Biochemical Oxygen Demand")
```

```{r}
data("Biochemical_Oxygen_Demand")
Biochemical_Oxygen_Demand
```

Suggested Usage
---------------
A simple quantitative dataset which can be used to show the relationship between two variables.  The data has no import problems and no NA values.

The timescale is discontinuous, with Time=6 missing.

The relationship between the points is not a simple linear relationship so this could be used as an example of a dataset where linear regression is not a great fit, even though R=0.8 and p=0.05.


Example Usage
-------------

### Quantitative relationship

```{r}
Biochemical_Oxygen_Demand %>%
  ggplot(aes(x=Time, y=Demand)) +
  geom_line(size=1) +
  geom_point(colour="red2", size=6) +
  ggtitle("Biochemical Oxygen Demand")
```

### Linear regression

```{r}
lm(Demand~Time, Biochemical_Oxygen_Demand) -> lm_result

lm_result
```

```{r}
cor.test(Biochemical_Oxygen_Demand$Demand,Biochemical_Oxygen_Demand$Time)
```


```{r}
Biochemical_Oxygen_Demand %>%
  ggplot(aes(x=Time, y=Demand)) +
  geom_line(size=1, colour="darkgrey") +
  geom_point(colour="#BB4444", size=4) +
  ggtitle("Linear Regression of Biochemical Oxygen Demand") +
  geom_abline(slope = lm_result$coefficients[2], intercept=lm_result$coefficients[1], size=2)
```