---
title: "Life Sciences Training Data"
output:
  html_document:
    df_print: paged
    toc: true
    css: "trainingdata.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```


Biomass_of_Herbivorous_Fish
===========================

```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----

```{r}
Training_Data_List %>%
  filter(startsWith(Data_set_Name,"Herbiverous"))
```

```{r}
data("Biomass_of_Herbivorous_Fish")
Biomass_of_Herbivorous_Fish
```


Suggested Usage
---------------
A more complicated, but still small, quantitative dataset with many independent variables and three categorical groups.  The data has some missing values.

Can be used to illustrate grouped colouring, for plotting means with measures of variance.

The deep and shallow mean biomasses show a linear releationship, but are more stable on a log scale

Example Usage
-------------

### Compare deep and shallow means

```{r}
Biomass_of_Herbivorous_Fish %>%
  ggplot(aes(x=Deep.Mean.Biomass, y=Shallow.Mean.Biomass, colour=Morpho.Functional.Group)) +
  geom_point(size=4) +
  ggtitle("Comparing Deep and Shallow Biomass") +
  geom_abline(slope=1,intercept=0)
```

### Compare deep vs shallow on a log scale

```{r}
Biomass_of_Herbivorous_Fish %>%
  ggplot(aes(x=Deep.Mean.Biomass, y=Shallow.Mean.Biomass, colour=Morpho.Functional.Group)) +
  geom_point(size=4) +
  ggtitle("Comparing Deep and Shallow Biomass") +
  geom_abline(slope=1,intercept=0)+
  scale_x_log10()+
  scale_y_log10()
```


### Labelling points
```{r}
library(ggrepel)
Biomass_of_Herbivorous_Fish %>%
  ggplot(aes(x=Deep.Mean.Biomass, y=Shallow.Mean.Biomass, colour=Morpho.Functional.Group, label=Species)) +
  geom_point(size=4) +
  ggtitle("Comparing Deep and Shallow Biomass") +
  geom_abline(slope=1,intercept=0)+
  geom_text_repel(colour="black")+
  scale_x_log10()+
  scale_y_log10()

```


### Plotting graphs with error bars
```{r}
Biomass_of_Herbivorous_Fish %>%
  ggplot(aes(
    x=Species,
    y=Shallow.Mean.Biomass,
    ymin=Shallow.Mean.Biomass - Shallow.Standard.Deviation.of.Biomass,
    ymax=Shallow.Mean.Biomass + Shallow.Standard.Deviation.of.Biomass,
    fill=Morpho.Functional.Group),
  ) +
  geom_col(colour="black") +
  geom_errorbar(width=0.3) +
  coord_flip()+
  scale_fill_brewer(palette="Set1")
```





