---
title: "Life Sciences Training Data"
output:
  html_document:
    df_print: paged
    toc: true
    css: "trainingdata.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```


Bird_Sighting_Texas_2018
========================

```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----
```{r}
Training_Data_List %>%
  filter(startsWith(Data_set_Name,"Birds Sighted"))
```

```{r}
data("Bird_Sighting_Texas_2018")
head(Bird_Sighting_Texas_2018,n=500)
```


Suggested Usage
---------------
A mostly qualitative dataset with several qualitative categories.  Can be used to aggregate multiple variables.  Comes with a text based date with inconsistent date formats which will be difficult to parse into usable quantitative dates.

Some species do not have a common name.

Some entries have neither a common name nor a taxon species name




Example Usage
-------------

### Different birds ever seen

```{r}
Bird_Sighting_Texas_2018 %>%
  distinct(common_name, .keep_all = TRUE) %>%
  select(-observed_on_string) %>%
  arrange(common_name)
```

### List of frequency of observation

```{r}
Bird_Sighting_Texas_2018 %>%
  group_by(common_name,taxon_species_name) %>%
  count() %>%
  arrange(desc(n))
```
### Make single name

```{r}
Bird_Sighting_Texas_2018 %>%
  filter(nchar(taxon_species_name) > 0) %>%
  mutate(has_common_name = nchar(common_name)>0) %>%
  group_by(has_common_name) %>%
  mutate(full_name=if_else(has_common_name,paste0(taxon_species_name," (",common_name,")"),taxon_species_name)) %>%
  ungroup() %>%
  select(full_name, common_name, taxon_species_name, everything()) -> Bird_Sighting_Texas_2018

head(Bird_Sighting_Texas_2018)
```

### Graph of frequency of observation
```{r}
set.seed(746)
Bird_Sighting_Texas_2018 %>%
  group_by(full_name) %>%
  count() %>%
  ungroup() %>%
  mutate(has_name=str_detect(full_name,"\\("))%>%
  group_by(has_name) %>%
  slice_sample(n=5) %>%
  ungroup()%>%
  arrange(n) %>%
  mutate(full_name=factor(full_name, levels=full_name)) %>%
  ggplot(aes(x=full_name,y=n)) +
  geom_col() +
  coord_flip()+
  ylab("Number of times observed") +
  xlab(NULL)
```

### Parsing the dates

Yeah, I should get around to writing this, but it's not going to be pretty...

