---
title: "Brain Bodyweight"
output:
  html_document:
    df_print: paged
    toc: true
    css: "trainingdata.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```


```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----
```{r}
Training_Data_List %>%
  filter(Data_set_Name=="Brain-Bodyweight Correlation")
```

```{r}
data("Brain_Bodyweight")
Brain_Bodyweight
```

Suggested Usage
---------------
This dataset illustrates the positive correlation between brainweight and bodyweight over a large number of species.

The relationship is roughly linear on a log scale.  Log transformed versions of the quantitative variables are provided but could also be calculated from the linear values.

The animals are grouped into Categories - the extinct animals have notably smaller brains for their bodyweight size.  This could be used to filter these samples, or to show that they are a significantly distinct group.


Example Usage
-------------

### Relationship on a linear scale

```{r}
Brain_Bodyweight %>%
  ggplot(aes(x=Brain.weight.g, y=Body.weight.kg, colour=Category)) +
  geom_point()
```

### Relationship on a log scale

```{r}
Brain_Bodyweight %>%
  ggplot(aes(x=log.brain.weight.g, y=Log.body.weight.kg, colour=Category)) +
  geom_point()
```

### Removing the extinct species

```{r}
Brain_Bodyweight %>%
  filter(Category != "Extinct") %>%
  ggplot(aes(x=log.brain.weight.g, y=Log.body.weight.kg, colour=Category)) +
  geom_point()
```

### Improved correlation without extinct

```{r}
cor.test(Brain_Bodyweight$Log.body.weight.kg, Brain_Bodyweight$log.brain.weight.g)
```

```{r}
Brain_Bodyweight %>%
  filter(Category != "Extinct") -> Brain_Bodyweight_No_Extinct

cor.test(Brain_Bodyweight_No_Extinct$Log.body.weight.kg, Brain_Bodyweight_No_Extinct$log.brain.weight.g)
```





