---
title: "Life Sciences Training Data"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

Modern_Pollen_Plant_Diversity_Relationships
===========================================

```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----
```{r}
Training_Data_List %>%
  filter(startsWith(Data_set_Name,"Modern"))
```


```{r}
data("Modern_Pollen_Plant_Diversity_Relationships")
Modern_Pollen_Plant_Diversity_Relationships
```

Suggested Usage
---------------
A dataset with lots of different quantitative variables with complex relationships.  Contains some genetic information as well as environmental and biological measures.

Several fields have missing values


Example Usage
-------------

### Tidy names
```{r}
str_replace(colnames(Modern_Pollen_Plant_Diversity_Relationships),"\\..*","") -> colnames(Modern_Pollen_Plant_Diversity_Relationships)
```

### Plot distributions
```{r}
Modern_Pollen_Plant_Diversity_Relationships %>%
  select(-Growth) %>%
  pivot_longer(cols=-Pollen, names_to="variable", values_to="value") %>%
  group_by(variable) %>%
  mutate(value=(value-min(value,na.rm = TRUE))/(max(value,na.rm=TRUE)-min(value,na.rm=TRUE))) %>%
  ungroup() %>%
  ggplot(aes(x=variable,y=value)) +
  geom_jitter(height=0, width=0.1) +
  ggtitle("Raw scaled distribtions")
```

### Plot disitributions after log transforming variables

```{r fig.width=9, fig.height=5}
Modern_Pollen_Plant_Diversity_Relationships %>%
  mutate(Seed=log2(Seed+0.1),SNPS=log2(SNPS+1)) %>%
  pivot_longer(cols=c(-Pollen,-Growth), names_to="variable", values_to="value") %>%
  group_by(variable) %>%
  mutate(value=(value-min(value,na.rm = TRUE))/(max(value,na.rm=TRUE)-min(value,na.rm=TRUE))) %>%
  ungroup() %>%
  ggplot(aes(x=variable,y=value, colour=Growth)) +
  geom_jitter(height=0, width=0.1) +
  ggtitle("Transformed scaled distribtions")
```


```{r}
Modern_Pollen_Plant_Diversity_Relationships %>%
  mutate(Seed=log2(Seed+0.1),SNPS=log2(SNPS+1)) -> Modern_Pollen_Plant_Diversity_Relationships
```

### Plot all correlations

```{r}
library(corrr)
Modern_Pollen_Plant_Diversity_Relationships %>%
  select(Seed:N) %>%
  correlate() %>%
  rplot()

```

### Look at a positive correlation

```{r}
lm(LDMC~Height,Modern_Pollen_Plant_Diversity_Relationships) -> ld_height_lm

ld_height_lm
```


```{r fig.height=6, fig.width=8}
Modern_Pollen_Plant_Diversity_Relationships %>%
  ggplot(aes(x=Height, y=LDMC, colour=Growth)) +
  geom_point() +
  geom_abline(intercept = ld_height_lm$coefficients[1], slope=ld_height_lm$coefficients[2], size=2, colour="red2")
```

### Look at negative correlation

```{r}
lm(LDMC~SLA,Modern_Pollen_Plant_Diversity_Relationships) -> ld_sla_lm

ld_sla_lm
```


```{r fig.height=6, fig.width=8}
Modern_Pollen_Plant_Diversity_Relationships %>%
  ggplot(aes(y=LDMC, x=SLA, colour=Growth)) +
  geom_point() +
  geom_abline(intercept = ld_sla_lm$coefficients[1], slope=ld_sla_lm$coefficients[2], size=2, colour="red2")
```