---
title: "Plant CO2 Uptake"
output:
  html_document:
    df_print: paged
    toc: true
    css: "trainingdata.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```


```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----
```{r}
Training_Data_List %>%
  filter(str_detect(Data_set_Name,"CO2"))
```


```{r}
data("Plant_CO2_Uptake")
Plant_CO2_Uptake
```

Suggested Usage
---------------
A concentration gradient linked to a quantitative uptake variable.  Categorical linkage to plants, types and whether they were chilled or not.  A nice dataset to show linked data (plant) with other possible confounding factors.  Could also be used to do curve fitting.




Example Usage
-------------

### Line graphs of major factors
```{r}
Plant_CO2_Uptake %>%
  ggplot(aes(x=conc,y=uptake, group=Plant, colour=Treatment)) +
  geom_line() +
  facet_wrap(vars(Type))
```

### Normalisation to lowest concentration

```{r}
Plant_CO2_Uptake %>%
  group_by(Plant) %>%
  mutate(norm_uptake=uptake-uptake[conc==95]) -> Plant_CO2_Uptake

Plant_CO2_Uptake
```
```{r}
Plant_CO2_Uptake %>%
  ggplot(aes(x=conc,y=norm_uptake, group=Plant, colour=Treatment)) +
  geom_line() +
  facet_wrap(vars(Type))
```

### Comparison at end points

```{r}
Plant_CO2_Uptake %>%
  filter(conc == max(conc)) %>%
  ggplot(aes(x=Type,y=norm_uptake, colour=Treatment)) +
  geom_jitter(size=4, height=0,width=0.3) +
  stat_summary(geom="errorbar", width=0.3, size=1)
```


