---
title: "Life Sciences Training Data"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

Sleep_Deprivation_CSD
=====================

```{r message=FALSE}
library(Trainingdata)
library(tidyverse)
theme_set(theme_bw(base_size=14))
```

Data
----
```{r}
Training_Data_List %>%
  filter(str_detect(Data_set_Name,"sleep"))
```


```{r}
data("Sleep_Deprivation_CSD")
Sleep_Deprivation_CSD
```

Suggested Usage
---------------
This is a small dataset comprising just a median, mean and standard deviation.  It's quite a nice demonstration of data where the mean is not a good summary of the data since the SD is huge comapared to the mean.  In the original paper the data is shown on a log scale which makes much more sense, but can't be used on the summarised values here.




Example Usage
-------------

### Plotting mean and SD

```{r}
Sleep_Deprivation_CSD %>%
  mutate(Group=factor(Group,levels=Group)) %>%
  ggplot(aes(x=Group, y=Mean.CSD.Threshold, ymin=Mean.CSD.Threshold-SD.CSD.Threshold, ymax=Mean.CSD.Threshold+SD.CSD.Threshold)) +
  geom_col() +
  geom_errorbar(width=0.4)
```



